### 2013-07-30 paper.tex
my feet are cold
Done.  FOREVER.

\section{Problem Statement}
\label{sec:probstate}
\begin{definition}
	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are \emph{orthogonal} if their product is zero.
\end{definition}
If we can find two half-maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.  More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.  In other words, any two maps with nonzero product can be used to construct an idempotent.

@@

Furthermore, I would like to thank my head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me, and the MIT Math Department for making my project possible.
I also wish to thank my tutor Mr. Antoni Rangachev, Northeastern University, for his invaluable advice in preparing both this paper and my final presentation.

>>>>

\section{Problem Statement}
\label{sec:probstate}
\begin{definition}
	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are \emph{orthogonal} if their product is zero.
\end{definition}
If we can find two half-maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.  More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.

@@

Furthermore, I would like to thank my head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me, and the MIT Math Department for making my project possible.
I also wish to thank my tutor Mr. Antoni Rangachev, Northeastern University, for his invaluable advice in preparing both this paper and my final presentation, as well as Felipe Hern\'andez and Charlie Pasternak for their revisions.
